Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-23 paper.tex
Remove repeat ADV definition

A wake map was generated by positioning a Nortek Vectrino+ acoustic Doppler
Velocimeter (ADV) at 270 different locations, varied in the cross-stream and
vertical directions at one turbine diameter downstream ($x/D=1$). These
locations have vertical coordinates from the turbine centerline up to
$z/H=0.625$, ranging in the cross-stream direction $y/R = \pm 3$. These
locations are shown in Figure~\ref{fig:wake-locations}.

>>>>

A wake map was generated by positioning the Vectrino probe at 270 different
locations, varied in the cross-stream and vertical directions at one turbine
diameter downstream ($x/D=1$). These locations have vertical coordinates from
the turbine centerline up to $z/H=0.625$, ranging in the cross-stream direction
$y/R = \pm 3$. These locations are shown in Figure~\ref{fig:wake-locations}.
